Interpretable Risk Minimization -- Preliminaries

### 2024-08-17 paper/main.tex
added BCE based loss, updated paper with OOD generalization result, updated hyperparameter

@@

\paragraph{Evaluating Generalization Capabilities} If we take another dog / cat dataset, could a well trained model perform better than traditional optimization, since it isn't relying as much on memorization of noise or distribution specific data?

>>>>

\subsection{Out-of-Distribution Generalization}

To test how well the approach generalizes out of the training distribution, we evaluate the performance of the binary classification contrastive model on random samples ($n=1000$) from the \href{https://www.microsoft.com/en-us/download/details.aspx?id=54765}{Kaggle Cats and Dogs Dataset}:
\begin{table}[h]
	\centering
	\begin{tabular}{c|c}
		\toprule
		\textbf{Method} & \textbf{Accuracy} \\
		\midrule
		Cross-Entropy & 49.5\% \\
		Interpretable (Ours) & \bf 78.5\% \\
		\bottomrule
	\end{tabular}
\end{table}

The next goal is to further understand and minimize this generalization gap.

@@
